---
title: "modelToolKitGuide"
author: "Matthew Davis"
date: "August 4, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model Tool Kit Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEngine{knitr::knitr}
---




#### Predictive Model Preformance 

Get predictive model prefomance by a catagory.  Check to see if a model is preforming differently in by a group or catagory

```{r setup, message=FALSE, comment='', results='hide' , fig.height=4, fig.width=6}
try(detach(package:modelToolKit, unload = TRUE))
library(modelToolKit)
library(treemap)
library(caret)
library(rpart)
data(iris)
set.seed(2012)
fit<-rpart(Species~., iris)
km<-kmeans(iris[,1:4], 3)
preds<-predict(fit, iris, type = 'class')
obs<-iris[,'Species']
cats<-as.factor(km$cluster)
```

plot preformance by class 

```{r}
x<-preformanceByCatagory(preds, obs, cats)
plot(x)
```



### Preformance by class in the case of regression models
```{r, message=FALSE,results='hide' , fig.height=4, fig.width=6}
data("Sacramento")
fit<-rpart(price~.,data = Sacramento )
preds<-predict(fit, Sacramento)
obs<-Sacramento[, 'price']
cats<-as.factor(Sacramento$city)
x<-preformanceByCatagory(preds, obs, cats ,catName = 'city' )
plot(x,2)
```


#### Cluster Model Utilities 

Assign new clusters using kmeans to new data 

```{r }
table(predictKmeans(km, iris)[,'cluster'])
x<-iris
x[,1]<-NA
table(predictKmeans(km, x)[, 'cluster'])
```

Find the optimal number of clusters
```{r, }
findClusters(iris[,1:4])
```
#### Data Frame and Factor Utlities 

Find differences between two factors 
```{r}
set.seed(12012)
x = as.factor(rep(c('a','b','c' , 'a'), 10))
y = as.factor(sample(c('a','b','c'), 30, replace = TRUE))
z<-factorDiffs(x,y)
z

```

Find difference between all factors in two data frames

```{r}
size = 100
df1<-data.frame(x = as.factor(sample(c('a','b','c' ,'d'),size, replace = TRUE)),
                y = as.factor(sample(c('a','b','c','a') ,size, replace = TRUE)))

df2<-data.frame(x = as.factor(sample(c('a','b','c','c'),size, replace = TRUE)),
                y = as.factor(sample(c('a','b','c','b'), size, replace = TRUE)))

dataFrameFactDiffs(df1, df2)
```



##### Dataframe Transforms

Reorder all factor levels accordning to frequency, 
works on a data frame or a factor 
```{r}
mydata<-data.frame(x = c(rep('a', 10),rep('b', 15), rep('c' , 10)),
                    y = c(rep('a', 10),rep('b', 5), rep('c' , 20)))
str(mydata)
str(reOrderAll(mydata))
```


Level Matcher Apply one set of levels to another data frame
In the case where levels are in the new data frame, but not in the original, the values are mapped to <NA>

```{r}
data1<-data.frame(x = as.factor(rep(c('a', 'b'), 10)), 
                  y =  as.factor(rep(c('c', 'd'), 10)))

data2<-data.frame(x = as.factor(rep(c('a', 'b', 'GG'), 10)), 
                  y =  as.factor(rep(c('c', 'FF','GG'), 10)))
str(levelMatcher(newData = data2, oldData = data1))
```


Map all values  NA values  unknown catagory or a specific number if numeric

```{r}
# create some data
mydata<-data.frame(x1 = rep(c('a', 'b', NA, 'c'),10),
                   x2 = rep(c('a', 'b', NA, 'c'),10),
                   y1 = rep(c(1,2,3,NA), 10),
                   y2 = rep(c(1,2,3,NA), 10))

head(NAtoValueDf(mydata, numVal = 0 , newLevName = 'unKnown' ), 10)

```


##### Variable Contributions


Generate a predictive model for housing price over the mean housing price using the Sacramento data set inside caret. This model will be used to demonstrate logistic difference between observation functions


```{r , message = FALSE}
library(caret)
library(ranger)
library(rpart)

data("Sacramento")
predVars<-c('city', 'beds', 'sqft','baths', 'type')
rd<-Sacramento[, predVars]
rd$class<-as.factor(ifelse(Sacramento$price > mean(Sacramento$price),1,0 ))
f<-formula(class~.)
fit<-glm(f, rd, family = 'binomial')

preds<-predict(fit, rd, type = 'response' )
fitranger<-ranger(f, rd, num.tree = 10, probability = TRUE, importance = 'impurity')
fitrpart<-rpart(f, rd)
```

Find the different factor contributions between a reference observation and a test observation. 
Uses a the most likely observation to test against. 
```{r}
logisticDifference(fitranger,rd[2,predVars], mydata =  rd )
```

Find the different factor contributions between a reference observation and a test data frame of observations. At the moment this does not scale very well.

```{r}
library(reshape)
library(modelToolKit)
x<-logisticDifferenceDf(model = fitranger,
                        testObs = rd[1:4,predVars],
                        refData = rd, 
                        p = .4,
                        verbose = TRUE )
print(x$output)
plot(x, indvidualPlot = TRUE, n.vars = 3)
```


