---
title: "modelToolKitGuide"
author: "Matthew Davis"
date: "August 4, 2017"
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
Get predictive model prefomance by a catagory
```{r setup, message=FALSE, comment=''}
try(detach(package:modelToolKit, unload = TRUE))
library(modelToolKit)
library(rpart)
data(iris)
set.seed(2012)
fit<-rpart(Species~., iris)
km<-kmeans(iris[,1:4], 3)
preds<-predict(fit, iris, type = 'class')
obs<-iris[,'Species']
cats<-as.factor(km$cluster)
preformanceByCatagory(preds, obs, cats)

```

Assign new clusters using kmeans to new data 

```{r }
head(predictKmeans(km, iris))
```

Find differences between data frames
```{r}

find2dfDiffs(iris[,1:4],iris[, 1:4]+.12)
```
Find the optimal number of clusters
```{r, }
findClusters(iris[,1:4])
```

Find differences between two factors 
```{r}
set.seed(12012)
x = as.factor(rep(c('a','b','c' , 'a'), 10))
y = as.factor(sample(c('a','b','c'), 30, replace = TRUE))
z<-factorDiffs(x,y)
z

```

Find differencew between all factors in two data frames
```{r}
size = 100
df1<-data.frame(x = as.factor(sample(c('a','b','c' ,'d'),size, replace = TRUE)),
                y = as.factor(sample(c('a','b','c','a') ,size, replace = TRUE)))

df2<-data.frame(x = as.factor(sample(c('a','b','c','c'),size, replace = TRUE)),
                y = as.factor(sample(c('a','b','c','b'), size, replace = TRUE)))

dataFrameFactDiffs(df1, df2)
```



Level Matcher Apply one set of levels to another data frame
```{r}
data1<-data.frame(x = as.factor(rep(c('a', 'b'), 10)), 
                  y =  as.factor(rep(c('c', 'd'), 10)))

data2<-data.frame(x = as.factor(rep(c('a', 'b', 'GG'), 10)), 
                  y =  as.factor(rep(c('c', 'FF','GG'), 10)))
str(levelMatcher(newData = data2, oldData = data1))
```
```{r cars}
library(caret)

data("Sacramento")
predVars<-c('city', 'beds', 'sqft','baths', 'type')
rd<-Sacramento[, predVars]
rd$class<-as.factor(ifelse(Sacramento$price > mean(Sacramento$price),1,0 ))
f<-formula(class~.)
fit<-glm(f, rd, family = 'binomial')

preds<-predict(fit, rd, type = 'response' )
```
check model preformance 
```{r}
cutoff = .5
postResample(as.factor(ifelse(preds > cutoff,1,0)), rd$class)
```
Find the different factor contributions between a reference observation and a test observation
```{r}
logisticDifference(fit,rd[2,predVars], mydata =  rd )
```
Find the different factor contributions between a reference observation and a test data frame of observations

```{r}
x<-logisticDifferenceDf(fit,rd[1:50,predVars], mydata =  rd, verbose = TRUE )
```

